---
title: "DEB.Model.1.1.2"
editor: visual
date: "2023-12-02"
author: "Emily Roberts"
subtitle: "Growth predictions from environmental conditions"
abstract: |
 I'm adding a MLE to estimate Xk. I'm not putting the model initialization for each initial length into the optimization function so that it can initialize correctly for all lengths and estimate multiple final lengths and optimize from all lengths. Fixed bug.

#format: html
format: 
  pdf:
    toc: TRUE
    number-sections: TRUE
    colorlinks: TRUE
---

### DEB code developed Summer 2018

Code DEB 3 state variables Emilien Pousse

DEB with pCO2 effect

```{r}
library(reshape2)
library(R.matlab)
library("ggplot2")

ScRCP = "Validation"
Zone = "Prov"
```

### Load packages, access files and DEB parameters

```{r}
dir_data <- "~/GitHub/EAD-ASEB-Ssolidissima-OA/projects/DEB/data/"
dir_data_biodep <- "~/GitHub/EAD-ASEB-Ssolidissima-OA/projects/Biodeposition/data/"
filename <- paste(dir_data,sep="","results_Ensis_directus.mat")
ParaMat=readMat(filename )
Param <- list()
```

##### Initialize *Spisula solidissima* parameters

Parameters from email correspondence 12/4/23

```{r}

Param$RhoV=15600; #(it is a general number for bivalves)
Param$GammaL1=0.8
Param$GammaL2=0.8
Param$v= 0.011 #cm/d Energy conductance
Param$Kappa=0.9607
Param$KappaX <- 0.8 #K Digestion efficiency of food
Param$Pm=10.64 #13.48
Param$Eg=2360 	 #2361
Param$Shape=0.32 #.32 is from surfclam field data (both sites) #Emilien used 0.37 
Param$s_M= 17.8 	 	 	 	#7.49598
Param$Pxm= 9.08/.8  	#30.6986/0.8
Param$Em=Param$Pxm*Param$KappaX/Param$v

#Arrhenius 5 parameter TPC
Param$Ta <- 9018 #K
Param$T1 <- 293.15 #K
Param$Tl <- 277.3 #K
Param$Th <- 296.5 #K
Param$Tal <- 15601 #K
Param$Tah <- 33775 #K

Param$Lp <- 3 #cm From Pousse et al. 2023
Param$dv <- 0.09 
Param$RhoE <- 19600 #J/g

#Parameters from conversation on GitHub on Jan 10, 2022
Param$pHl <- 1011 #uatm Lower pCO2 boundary for ingestion
Param$pHh <- 6778 #uatm Higher pCO2 boundary for ingestion

Param$MpHl <- 700 #uatm Lower pCO2 boundary for maintenance costs
Param$MpHh <- 1300 #uatm Higher pCO2 boundary for maintenance costs
```

##### Initialize *Spisula solidissima* pH parameters

```{r}
Param$del_pH=0.009 #Corrected according to email/table values 2/9/23
```

##### Chose the date when you want the model to start

This will set different temperature and pCO2 forcing variables

```{r}
Oyster='now'# now; 2045; 2070; 2095
```

### Read in Cape Cod data

Load CapeCod estimates

```{r}
CapeCod_dir <- "~/GitHub/EAD-ASEB-Ssolidissima-OA/projects/DEB/data/Transplant_test_dummy_data/"
biometrics_data <- read.csv(paste(CapeCod_dir,"Lengths.csv",sep = "")) #Biometrics
environ_data <- read.csv(paste(CapeCod_dir,"Environ.csv",sep = "")) #Environment

POM_raw.Eel <- read.csv("~/GitHub/EAD-ASEB-Ssolidissima-OA/projects/Seawater data/data/TSM and Chl/Output_data/dailyPOMest.Eel.csv") #POM
POM_raw.Prov <- read.csv("~/GitHub/EAD-ASEB-Ssolidissima-OA/projects/Seawater data/data/TSM and Chl/Output_data/dailyPOMest.Prov.csv") #POM

pCO2.E <- read.csv("~/GitHub/EAD-ASEB-Ssolidissima-OA/projects/Seawater data/data/Carbonate chem/pCO2.est.E.csv")
pCO2.P <- read.csv("~/GitHub/EAD-ASEB-Ssolidissima-OA/projects/Seawater data/data/Carbonate chem/pCO2.est.P.csv")

Temp.E <- read.csv("~/GitHub/EAD-ASEB-Ssolidissima-OA/projects/Seawater data/data/Carbonate chem/Temp.est.E.csv")
Temp.P <- read.csv("~/GitHub/EAD-ASEB-Ssolidissima-OA/projects/Seawater data/data/Carbonate chem/Temp.est.P.csv")

Growth.all <- read.csv("~/GitHub/EAD-ASEB-Ssolidissima-OA/projects/Transplant_growth_survival/data/Growth.est.len.csv", stringsAsFactors = FALSE)
Growth.E<- Growth.all[Growth.all$Site=="Eel Pond",]
Growth.P<- Growth.all[Growth.all$Site=="Ptown",]

head(POM_raw.Eel)

head(pCO2.E)
```

### Cape Cod data temporal vector

Make the temporal vector. Here I'm using tester data that is 20 days long, so made my start and stop dates match.

```{r}
if(Zone=='Prov'){
  Oyster="nul"
  date_start<-"09/27/2022"# Select a start date format = dd/mm/yyyy
  date_end<-"6/09/2023"
  date_start <- as.Date(strptime(date_start,tz="UTC",format="%m/%d/%Y"))
  date_end <- as.Date(strptime(date_end,tz="UTC",format="%m/%d/%Y"))
  MABpCO2.P=pCO2.P$y[as.Date(pCO2.P$x)>=date_start&as.Date(pCO2.P$x)<=date_end]
  pH=MABpCO2.P 
  Food <- POM_raw.Prov$y[as.Date(POM_raw.Prov$x)>=date_start&
                           as.Date(POM_raw.Prov$x)<=date_end]
  Temp <- Temp.P$x[as.Date(Temp.P$Date)>=date_start&
                     as.Date(Temp.P$Date)<=date_end]+273 
  Growth <- Growth.P
  Param$Xk=1.8 #Initial starting value for mle
}

if(Zone=='Eel'){
  Oyster="nul"
  date_start<-"09/27/2022"# Select a start date format = dd/mm/yyyy
  date_end<-"6/09/2023"
  #date_start <- as.Date(strptime(date_start,tz="UTC",format="%m/%d/%Y"))
  #date_end <- as.Date(strptime(date_end,tz="UTC",format="%m/%d/%Y"))
  date_start <- as.Date(strptime(date_start,tz="UTC",format="%m/%d/%Y"))
  date_end <- as.Date(strptime(date_end,tz="UTC",format="%m/%d/%Y"))
  MABpCO2.E=pCO2.E$y[as.Date(pCO2.E$x)>=date_start&as.Date(pCO2.E$x)<=date_end]
  pH=MABpCO2.E 
  Food <- POM_raw.Eel$y[as.Date(POM_raw.Eel$x)>=date_start&
                          as.Date(POM_raw.Eel$x)<=date_end]
  Temp <- Temp.E$x[as.Date(Temp.E$Date)>=date_start&
                     as.Date(Temp.E$Date)<=date_end]+273
  Growth <- Growth.E
  Param$Xk=1.8 #Initial starting value for mle
  }

 
  #date_start <- as.numeric(strptime(date_start,tz="UTC",format="%m/%d/%Y"))
  #date_end <- as.numeric(strptime(date_end,tz="UTC",format="%m/%d/%Y"))

 dt   <- 86400  # The timestep in seconds, set to 1 day 
                #(3600s = 1h / 86400s = 1day / 28800 = 8h )
 pdt  <- 1 # The time step in days, set to 1 day (= unité de paramètres du DEB)
 Xnum <- seq(from = as.numeric(date_start),as.numeric(date_end))#vector with each time step (sec) #Was seq(from = date_start,date_end,dt), but this doesn't makes sense for our code. The timestep just needs to be in days -ER 2/8/24
 
 Xtps <- as.POSIXct(Xnum,origin='1970-1-1',tz="UTC")#vector with each time step (normal date)
 ndt  <- length(Xnum)# Number of days
# ndt=9125

 
length(Temp)
length(Food)
length(pH)
ndt
```

#### Verification of the forcing variables

Check if all the forcing variables have the same length or have missing values

```{r}
if (length(Temp) <= 1 || length(Temp) != length(Food)) {
  stop("Arguments Temp / Food / T_im have different lengths: ",length(Temp)," ; ",length(Food))
}
if (TRUE %in% is.na(Temp) || TRUE %in% is.na(Food)) {
  stop(" Arguments Temp, Food and T_im must not have missing values.")
}# Just to confirm that forcing variables are correct

```

### Get initial values

Note - our surfclams start around a size of 1cm length as well, so this can be used without much modification.

```{r}
Init=c()
Eri=c()
Ei=c()
Vi=c()
DFMi=c()
Li=c()

```

```{r}
#nbAnim <- 2#max(Init$id)

Growth <- Growth[Growth$Collection.month=="Jun",]

nbAnim <- length(Growth$Li)
id=seq(1:nbAnim)

p <- 1
for (p in 1:nbAnim){
  e=0.2#0.57 #Density of reserve: 1=full, 0=empty, rule: 0.2 winter, 0.6 summer 0.4 fall/spring
  Li[p]   = Growth$Li[p]/10 #In cm
  Vi[p]   = (Li[p] * Param$Shape)^3
  Ei[p]=Param$RhoE*(8.18e-6-(Vi[p]*0.09))
  
  # if(Vi[p]>(Param$Lp*Param$Shape)^3){Eri[p]= ((phys$DFM[p] - (Vi[p] *Param$dv)) * Param$RhoE - Ei[p])
  # }else{Eri[p]=0
  # Ei[p]= max(c(0.000001,(phys$DFM[p]-Vi[p]*Param$dv)*Param$RhoE))} 
  #Initial Ei is from DFM = E+V. E = Ei + Eir. If not reproductive then Eir = 0. I think max 0.000001 is set up to avoid the problem that Ei could be set to 0 inadvertantly. 
  
# if(Vi[p]>(Param$Lp*Param$Shape)^3){print("adult, determine dry flesh weight")
#    }else{Eri[p]=0
#    Ei[p]= max(c(0.000001,(phys$DFM[p]-Vi[p]*Param$dv)*Param$RhoE))} 
  
  Eri[p]=0
  Ei[p]= .01*Vi[p]*Param$dv*Param$RhoE #MAR - set Ei as 1/100 of Vi. Fill in later using equation above using the dry weight at the start of the experiment. 
  
  if(Eri[p]<=0){Eri[p]=0}

  DFMi[p] = ((Ei[p] + Eri[p])/Param$RhoE + Param$dv*Vi[p])
}
Init=as.data.frame(cbind(id,Li,Vi,Ei,Eri,DFMi))#,Egoi))


  
```

"nbAnim" is the ID of the animal and/or simulation. Here there are two simulations, one for MAB and one for GB, and they are given the same starting lengths. Provincetown and Eel Pond will be two locations, and we can fit these runs to three independent data collections each for the three growth measurements. I'd like to start with this second experiment because temps also will be in the range for where we have data.

### DEB model simulations

Creation of the results database and launch DEB for each individual

Number of returned parameters for fCalcDEB_4VE = 21

```{r}
Result<-array(NA, dim=c(ndt, 20, nbAnim)) # Make a 3D matrix [time, output value, individual]
colnames(Result)<-c("jour","E","V","Er","DFM","L","e","PM","Pc1","f","Pg","Pa","Temp","cT","Xnum","Pl1","Pl2","Pm1","Pj","Pr")#name the parameters
n_iter <- length(Temp)
ErBalance=matrix(0,ncol=n_iter/365,nrow=nbAnim)
```

Here modifying the code for simplicity, since nbAnim is set to 2

for (i in 1:nbAnim) {}

### Temperature correction

```{r}
cT<-exp((Param$Ta /Param$T1)-(Param$Ta /Temp)) *
  (1+exp((Param$Tal/Param$T1)-(Param$Tal/Param$Tl))+exp((Param$Tah/Param$Th)-(Param$Tah/Param$T1)))/
  (1+exp((Param$Tal/Temp)-(Param$Tal/Param$Tl))+exp((Param$Tah/Param$Th)-(Param$Tah/Temp    ))) 

```

```{r}
 Xk <- 1.8
 Param <- Param[-27]
```

```{r}

    DEB_model_run <- function(par=par, Init=Init, Food=Food, Temp=Temp, 
                              ndt=ndt, Param=Param, cT=cT, pH=pH, pdt=pdt, 
                              Result=Result, Xnum=Xnum) {
      i <- 1
      ## Initialisation du DEB
      for(i in 1:dim(Result)[3]){
      L = Init$Li[i]
      V = Init$Vi[i]
      E   = Init$Ei[i] 
      Er  = Init$Eri[i]
      DFM = Init$DFMi[i]
      
      Xk = par[1]
 
      
      vecteur_f   = Food/(Food+Xk)
      #vecteur_f   = Food/(Food+Param$Xk)
      
      
      
        ## Initialisation des sorties / energy expenditures
    #############################
    # nombre d'itération
    n_iter = length(Temp)
    # Création de vecteurs contenant les variables d'état
    vecteur_E   = vector("numeric",length=n_iter)
    vecteur_V   = vector("numeric",length=n_iter)
    vecteur_Er  = vector("numeric",length=n_iter)
    vecteur_temps = vector("numeric",length=n_iter) 
    
    # Initialization of the state variables
    vecteur_E[1]=E[1]
    vecteur_V[1]=V[1]
    vecteur_Er[1]=Er[1]
    
    vecteur_temps[1]=0    ####################Utile?
    Balance=0
    
    vecteur_Pa   = vector("numeric",length=n_iter)
    vecteur_Px   = vector("numeric",length=n_iter)
    vecteur_PM   = vector("numeric",length=n_iter)
    vecteur_Pc1  = vector("numeric",length=n_iter)
    vecteur_Pg   = vector("numeric",length=n_iter)
    vecteur_Pr   = vector("numeric",length=n_iter)
    vecteur_Pj   = vector("numeric",length=n_iter)
    vecteur_Pl1  = vector("numeric",length=n_iter)
    vecteur_Pl2  = vector("numeric",length=n_iter)
    vecteur_Pm1  = vector("numeric",length=n_iter)
    vecteur_Em  = vector("numeric",length=n_iter)#################### utile?
    vecteur_cpH  = vector("numeric",length=n_iter)
    vecteur_cpH_feed  = vector("numeric",length=n_iter)

      
  
    
      ## Start of the calculation loop
      ################################
      #for (n in 1:n_iter){
    n <- 1
    for (n in 1:ndt){
        #### Correction of biological functions impacted by Temperature  
        Pxm =  Param$Pxm* cT[n]*Param$s_M
        Pm=Param$Pm* cT[n] 
        v = Param$v* cT[n] * Param$s_M
        
        
        # Compound parameters corrected  
        Pam = Pxm * Param$KappaX
        Em  = Pam/v
        KappaG = (Param$dv*Param$RhoV)/Param$Eg
        Vp = (Param$Shape*Param$Lp)^3
        if(pH[n]<=1011){cpH=1}else{cpH=(Param$pHh-pH[n])/(Param$pHh-Param$pHl)}
        vecteur_cpH[n] <- cpH
        
        Px  <- Pxm * vecteur_f[n] * V^(2/3)  #Ingestion
        
        Pa  <- Pxm * vecteur_f[n] * V^(2/3) * Param$KappaX *cpH
    
        
        Pc1 <- E * (((Param$Eg * (v/V^(1/3))) + Pm) / (Param$Eg + (Param$Kappa * (E/V))))#Mobilization from E
    
        cpH_feed <- Param$del_pH*
                       (min(max(pH[n]-Param$MpHl,0),Param$MpHh-Param$MpHl))
        vecteur_cpH_feed[n] <- cpH_feed

        
        PM  <- (Pm * V)+cpH_feed*V^(2/3)*cT[n]#Maintenance costs 
    
        Pm1 <- min(PM,Param$Kappa * Pc1) #maintenance costs paid
        
        Pg  <- Param$Kappa * Pc1 - Pm1 #Growth
        
        Pj  <- min(c(V,Vp)) * Pm * ((1 - Param$Kappa) / Param$Kappa) #Maturation
        
        Pr   <- max(c((1 - Param$Kappa)*Pc1 - Pj,0)) # Reproduction
        
        
        
    
        #SANS GONADE
        # In case of long starvation (i.e. maintenance costs cannot be paid):
        if(Param$Kappa*Pc1<=PM){# Maintenance costs cannot be paid
          E  = max(0, E   + (Pa - Pc1) * pdt)
          Pl2=1/Param$GammaL2*(PM-(Param$Kappa*Pc1))
          Pr=0
          if(V>=Vp&Er>=Pl2){
            Er=max(0, Er  - Pr-Pl2 * pdt)
            V  = max(0, V)
          }else{
            Pl1=1/Param$GammaL1*(PM-Param$Kappa*Pc1)
            Er=0
            V  = max(0, V   + (-Pl1)/(Param$RhoV*Param$dv) * pdt)
            Pl2=0
          }
    
        }else{
          Pl1=0
          Pl2=0
          # State variables calculation
          E  = max(0, E   + (Pa - Pc1) * pdt)
          V  = max(0, V   + (Pg/Param$Eg-Pl1) * pdt)
          Er = max(0, Er  + (Pr - Pl2) * pdt)
          if(V<Vp){Er=0}}
        
        ## More outputs 
        ###############
        DFM = (E+Er)/Param$RhoE + Param$dv*V #+ Ego*Param$dgo/Param$EGgo# Dry flesh mass
        if(V^(1/3)/Param$Shape>=L){
          L=V^(1/3)/Param$Shape
        }
        e = (E/V)/Em 
        
        
        # State variables allocation
        vecteur_E[n]   = E
        vecteur_V[n]   = V
        vecteur_Er[n]  = Er
        
        # Output variables
        vecteur_temps[n]= n*pdt
        vecteur_Pa[n]   = Pa
        vecteur_Px[n]   = Px
        vecteur_Pr[n]   = Pr
        vecteur_Pj[n]   = Pj
        vecteur_PM[n]   = PM
        vecteur_Pc1[n]  = Pc1
        vecteur_Pg[n]   = Pg
    
        vecteur_Pl1[n]  =Pl1
        vecteur_Pl2[n]  =Pl2
        vecteur_Pm1[n]  =Pm1
        
        #Result[n,1:20,i]=c(n,E,V,Er,DFM,L,e,PM,Pc1,vecteur_f[n],Pg,Pa,Temp[n],cT[n],Xnum[n],Pl1,Pl2,Pm1,Pj,Pr)
        Result[n,1:20,i]=c(n,E,V,Er,DFM,L,e,PM,Pc1,vecteur_f[n],Pg,Pa,Temp[n],cT[n],Xnum[n],Pl1,Pl2,Pm1,cpH, cpH_feed)
        #Length[i] <- Result[[ndt,6,i]]
        #print(paste("/ timestep",n))
         } 
        #print(paste("/ ind.",i)) #Individual 1
  
       } 
     return(Result)
    }

    Result.check <- DEB_model_run(Init = Init,par= c(Xk = 5,sigma = .5), Food=Food, Temp=Temp, ndt=ndt, Param=Param, cT=cT, pH=pH, pdt=pdt, Result=Result, Xnum=Xnum)

    nbAnim <- dim(Result.check)[3]
    Length <- rep(NA,times = nbAnim)
    (Length <- as.vector(Result.check[ndt,6,][1:nbAnim]))

    
    
  NLL_Xk <- function(par=par, data_len=data_len, Init = Init, Food=Food, Temp=Temp, 
                                ndt=ndt, Param=Param, cT=cT, pH=pH, pdt=pdt, 
                                Result=Result, Xnum=Xnum) {
    
    Result.out <- DEB_model_run(Init = Init, par=par, Food=Food, Temp=Temp, 
                                ndt=ndt, Param=Param, cT=cT, pH=pH, pdt=pdt, 
                                Result=Result, Xnum=Xnum)
    sigma = par[2]
    nbAnim <- dim(Result.out)[3]
    Length <- rep(NA,times = nbAnim)
    Length <- as.vector(Result.out[ndt,6,][1:nbAnim])
    
    NLL <- -sum(dnorm(x = data_len, mean = Length, sd = sigma, log = TRUE))
    return(NLL)
   }


```

```{r}
initial_guess <- c(Xk = 3, sigma = 1)
str(initial_guess[1])

par <- initial_guess

if(Zone == "Eel"){
MLE.E <- optim(
      par = initial_guess, 
      lower=c(.01,.001),
      upper=c(100,100),
      method="L-BFGS-B",
      data_len = Growth.E$Lf[Growth.E$Collection.month=="Jun"]/10,
      fn = NLL_Xk, 
      Food=Food, 
      Param=Param, 
      ndt=ndt, 
      cT=cT, 
      pH=pH, 
      Init = Init,
      pdt=pdt, 
      Result=Result, 
      Temp=Temp, 
      Xnum=Xnum
      )
MLE <- MLE.E
}

#      Xk    sigma 
#15.83707  0.10000 


if(Zone == "Prov"){
MLE.P <- optim(
      par = initial_guess, 
      lower=c(1,.001),
      upper=c(10,100),
      method="L-BFGS-B",
      fn = NLL_Xk, 
      data_len=Growth.P$Lf[Growth.P$Collection.month=="Jun"]/10, 
      Init = Init, Food=Food, 
      Temp=Temp, 
      ndt=ndt, 
      Param=Param, 
      cT=cT, 
      pH=pH, 
      pdt=pdt, 
      Result=Result,
      Xnum=Xnum
      
      
      )
MLE <- MLE.P
}

# $par
#       Xk    sigma 
# 5.201025 0.100000

MLE

```

Use MLE output to calculate results

```{r}


# str(Result) 
# 
# Result[1,,]
# Result[,,1]
# 
# 
# 
# if(Zone == "Prov"){
# 
# Result.ar.P <- array(unlist(Result), dim = dim(Result))
#     
#     #nbAnim <- dim(Result.out)[3]
#     #Length <- rep(NA,times = nbAnim)
#     Length <- Result.ar.P[ndt,6,1:nbAnim]
# }
#     
if(Zone == "Prov"){
  Result.out <- DEB_model_run(Init = Init, par= MLE.P$par, Food=Food, Temp=Temp, 
                              ndt=ndt, Param=Param, cT=cT, pH=pH, pdt=pdt, 
                              Result=Result, Xnum=Xnum)
  Result.out.P <- Result.out
  #write.csv(as.data.frame(Result.P), file = "~/GitHub/EAD-ASEB-Ssolidissima-OA/projects/DEB/data/Prov.result.csv")
}

if(Zone == "Eel"){
    Result.out <- DEB_model_run(Init = Init, par=MLE.E$par, Food=Food, Temp=Temp, 
                                ndt=ndt, Param=Param, cT=cT, pH=pH, pdt=pdt, 
                                Result=Result, Xnum=Xnum)
  Result.out.E <- Result.out
  #write.csv(as.data.frame(Result.E), file = "~/GitHub/EAD-ASEB-Ssolidissima-OA/projects/DEB/data/Eel.result.csv")

}
  Length_out.P <- Result.out.P[,6,1][1:ndt]
  Pa_out.P <- Result.out.P[,12,][1:ndt]
  Day.P <-  Result.out.P[,1,][1:ndt]
  Length_out.E <- Result.out.E[,6,1][1:ndt]
  Pa_out.E <- Result.out.E[,12,][1:ndt]
  Day.E <-  Result.out.E[,1,][1:ndt]

    
#Result.E <- read.csv("~/GitHub/EAD-ASEB-Ssolidissima-OA/projects/DEB/data/Eel.result.csv",stringsAsFactors = FALSE)
#Result.P <- read.csv("~/GitHub/EAD-ASEB-Ssolidissima-OA/projects/DEB/data/Prov.result.csv",stringsAsFactors = FALSE)


```

```{r}
Result.out[1,,1]
Length_out <- Result.out[,6,1][1:ndt]
Pa_out <- Result.out[,12,][1:ndt]
Day <-  Result.out[,1,][1:ndt]

# plot(Day/365,Pa_out,type='l',lwd=2,
#          #ylim=c(0,20),xlim=c(0,25),
#          #ylab=ylabel,cex.lab=2,
#          xlab="Time (y)",cex.axis=2)
#      #,xlim=c(0,length(Resultmean)/365+0.25))
#    #text(0,19.5,"(B)")
# 
# plot(Day.P/365,Length_out.P,type='l',lwd=2,
#          #ylim=c(0,20),xlim=c(0,25),
#          #ylab=ylabel,cex.lab=2,
#          xlab="Time (y)",cex.axis=2)
#      #,xlim=c(0,length(Resultmean)/365+0.25))
#    #text(0,19.5,"(B)")
# 
# points(Day.E/365,Length_out.E,type='l',lwd=2,
#          #ylim=c(0,20),xlim=c(0,25),
#          #ylab=ylabel,cex.lab=2,
#          xlab="Time (y)",cex.axis=2)
#      #,xlim=c(0,length(Resultmean)/365+0.25))
#    #text(0,19.5,"(B)")

nbAnim.P <- dim(Result.out.P)[3]
Length_f <- Result.out.P[ndt,6,][1:nbAnim.P]
Length_i <- Result.out.P[1,6,][1:nbAnim.P]
Growth.pred.P <-Length_f-Length_i

nbAnim.E <- dim(Result.out.E)[3]
Length_f <- Result.out.E[ndt,6,][1:nbAnim.E]
Length_i <- Result.out.E[1,6,][1:nbAnim.E]
Growth.pred.E <-Length_f-Length_i

Growth.obs.P <- (Growth.P$Lf[Growth.P$Collection.month=="Jun"]-
                   Growth.P$Li[Growth.P$Collection.month=="Jun"])/10

Growth.obs.E <- (Growth.E$Lf[Growth.E$Collection.month=="Jun"]-
                   Growth.E$Li[Growth.E$Collection.month=="Jun"])/10

plot(Growth.pred.P~Growth.obs.P, ylim = c(0,3), xlim = c(0,3), col = "darkgreen", pch = 21, ylab = "Predicted growth (cm)", xlab = "Observed growth (cm)")
points(Growth.pred.E~Growth.obs.E,  col = "orange", pch = 21)

```

```{r}

arr_long.E <- reshape2::melt(Result.out.E[,6,])
arr_long.P <- reshape2::melt(Result.out.P[,6,])
arr_long.E <- cbind(arr_long.E, Site = rep("Eel",times = nrow(arr_long.E)))
arr_long.P <- cbind(arr_long.P, Site = rep("Prov",times = nrow(arr_long.P)))
arr_long <- rbind(arr_long.E, arr_long.P)
head(arr_long.P)
names(arr_long) <- c("Day","nbAnim","Length","Site")
ggplot(arr_long, aes(x=Day, y = Length, group = nbAnim))+
  geom_line(aes(color = as.factor(nbAnim)))+
  facet_wrap(~Site)+
  theme_classic()


```

```{r}
head(Result.out.E)
arr_long.E <- reshape2::melt(Result.out.E[,14,])
arr_long.P <- reshape2::melt(Result.out.P[,14,])
arr_long.E <- cbind(arr_long.E, Site = rep("Eel",times = nrow(arr_long.E)))
arr_long.P <- cbind(arr_long.P, Site = rep("Prov",times = nrow(arr_long.P)))
arr_long <- rbind(arr_long.E, arr_long.P)
head(arr_long.P)
names(arr_long) <- c("Day","nbAnim","cT","Site")
ggplot(arr_long, aes(x=Day, y = cT, group = nbAnim, color = Site))+
  geom_line(aes(color = as.factor(nbAnim)))+
  theme_classic()
  #facet_wrap(~Site)
```

```{r}
head(Result.out.E)
arr_long.E <- reshape2::melt(Result.out.E[,19,])
arr_long.P <- reshape2::melt(Result.out.P[,19,])
arr_long.E <- cbind(arr_long.E, Site = rep("Eel",times = nrow(arr_long.E)))
arr_long.P <- cbind(arr_long.P, Site = rep("Prov",times = nrow(arr_long.P)))
arr_long <- rbind(arr_long.E, arr_long.P)
head(arr_long.P)
names(arr_long) <- c("Day","nbAnim","cT","Site")
ggplot(arr_long, aes(x=Day, y = cT, group = nbAnim, color = Site))+
  geom_line(aes(color = as.factor(nbAnim)))+
  theme_classic()
  facet_wrap(~Site)
```

```{r}
plot(pH)

head(Result.out.E)
arr_long.E <- reshape2::melt(Result.out.E[,8,])
arr_long.P <- reshape2::melt(Result.out.P[,8,])
arr_long.E <- cbind(arr_long.E, Site = rep("Eel",times = nrow(arr_long.E)))
arr_long.P <- cbind(arr_long.P, Site = rep("Prov",times = nrow(arr_long.P)))
arr_long <- rbind(arr_long.E, arr_long.P)
head(arr_long.P)
names(arr_long) <- c("Day","nbAnim","cT","Site")
ggplot(arr_long, aes(x=Day, y = cT, group = nbAnim, color = Site))+
  geom_line(aes(color = as.factor(nbAnim)))+
  theme_classic()
  #facet_wrap(~Site)

```

```{r}

```

```{r}

MABpCO2.E.new <- cbind(MABpCO2.E, Site = rep("Eel",times = nrow(arr_long.E)))
MABpCO2.P.new <- cbind(MABpCO2.P, Site = rep("Prov",times = nrow(arr_long.P)))
arr_long <- as.data.frame(rbind(MABpCO2.E.new[,c(1:2)], MABpCO2.P.new[,c(1:2)]))
names(arr_long)<- c("pCO2","Site")

arr_long$Site <- as.factor(arr_long$Site)
arr_long$pCO2 <- as.numeric(arr_long$pCO2)
arr_long$Site <- factor(arr_long$Site, levels=c('Prov', 'Eel'))


ggplot(arr_long , aes(x=pCO2, fill=Site)) +
    geom_histogram(binwidth=50, alpha=.5, position="identity")+
  theme_classic()+
  geom_vline(aes(xintercept=700),   # Ignore NA values for mean
               color="black", linetype="dashed", size=1)+
  geom_vline(aes(xintercept=1011),   # Ignore NA values for mean
               color="black", linetype="solid", size=1)+ 
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0))

```

```{r}
Temp.E.new <- cbind(Temp, Site = rep("Eel",times = nrow(arr_long.E)))
Temp.P.new <- cbind(Temp, Site = rep("Prov",times = nrow(arr_long.P)))
arr_long <- as.data.frame(rbind(Temp.new[,c(1:2)], Temp.P.new[,c(1:2)]))
names(arr_long)<- c("pCO2","Site")

arr_long$Site <- as.factor(arr_long$Site)
arr_long$pCO2 <- as.numeric(arr_long$pCO2)
arr_long$Site <- factor(arr_long$Site, levels=c('Prov', 'Eel'))


ggplot(arr_long , aes(x=pCO2, fill=Site)) +
    geom_histogram(binwidth=50, alpha=.5, position="identity")+
  theme_classic()+
  geom_vline(aes(xintercept=700),   # Ignore NA values for mean
               color="black", linetype="dashed", size=1)+
  geom_vline(aes(xintercept=1011),   # Ignore NA values for mean
               color="black", linetype="solid", size=1)+ 
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0))
```
